Sparse spectral and $p$-finite element methods on disk-slices and trapeziums I: zero boundary conditions

### 2019-04-03 papers/halfdisk/halfdisk.tex
Minor edit

\begin{figure}
	\begin{subfigure}[t]{0.3\textwidth}
	\includegraphics[scale=0.3]{solution}
	\centering
	\caption{}
        	\label{fig:solution-poisson}
	\end{subfigure}
	\begin{subfigure}[t]{0.4\textwidth}
        	\includegraphics[scale=0.4]{solutionblocknorms}
	\centering
	\caption{}
        	\label{fig:solutionblocknorms}
	\end{subfigure}
	\caption{(a) The computed solution to $\Delta u = f$ with zero boundary conditions with $f(x,y) = 1 + \text{erf}(5(1 - 10((x - 0.5)^2 + y^2)))$. (b) The norms of each block of the computed solution of the Poisson equation with the given right hand side functions.}
	\centering
\end{figure}

@@

We can tackle the problem as follows. Fix \(a, b = 1,1\). Denote the coefficient vector for expansion of $u$ in the $\bigWii$ OP basis up to degree $N$ by $\mathbf{u}$, and the coefficient vector for expansion of $f$ in the $\bigPii$ OP basis up to degree $N$ by $\mathbf{f}$. Since $f$ is known, we can obtain $\mathbf{f}$ using the quadrature rule above. In matrix-vector notation, our system hence becomes:
\begin{align}
    \laplacewii \mathbf{u} = \mathbf{f}
\end{align}
which can be solved to find $\mathbf{u}$.
In Figure \ref{fig:solution-poisson} we see the solution to the Poisson equation with zero boundary conditions given in (\ref{eqn:poisson}) in the half-disk $\Omega$. In Figure \ref{fig:solutionblocknorms} we show the norms of each block of calculated coefficients of the approximation for four right-hand sides of the Poisson equation with N = 200. The rate of decay in the coefficients is a proxy for the rate of convergence of the computed solution. \bstodo{Describe what plot tells us}

>>>>

\begin{figure}
	\includegraphics[scale=0.3]{solution}
	\centering
	\caption{The computed solution to $\Delta u = f$ with zero boundary conditions with $f(x,y) = 1 + \text{erf}(5(1 - 10((x - 0.5)^2 + y^2)))$.}
        	\label{fig:solution-poisson}
	\centering
\end{figure}

@@

We can tackle the problem as follows. Fix \(a, b = 1,1\). Denote the coefficient vector for expansion of $u$ in the $\bigWii$ OP basis up to degree $N$ by $\mathbf{u}$, and the coefficient vector for expansion of $f$ in the $\bigPii$ OP basis up to degree $N$ by $\mathbf{f}$. Since $f$ is known, we can obtain $\mathbf{f}$ using the quadrature rule above. In matrix-vector notation, our system hence becomes:
\begin{align}
    \laplacewii \mathbf{u} = \mathbf{f}
\end{align}
which can be solved to find $\mathbf{u}$.
In Figure \ref{fig:solution-poisson} we see the solution to the Poisson equation with zero boundary conditions given in (\ref{eqn:poisson}) in the half-disk $\Omega$. In Figure \ref{fig:solutionblocknorms} we show the norms of each block of calculated coefficients of the approximation for four right-hand sides of the Poisson equation with N = 200. The rate of decay in the coefficients is a proxy for the rate of convergence of the computed solution. We see that\bstodo{Describe what plot tells us}

\begin{figure}
        	\includegraphics[scale=0.5]{solutionblocknorms}
	\centering
	\caption{The norms of each block of the computed solution of the Poisson equation with the given right hand side functions.}
        	\label{fig:solutionblocknorms}
\end{figure}
